Learning Discrete Bayesian Networks from Continuous Data

### 2017-05-11 jair_Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
YC update
typo

The two factors on the right hand side come from the second principle: all distributions of values of the parents of $\cX$ in a given interval are equiprobable.
The fourth principle is that the distributions for each interval are independent, so the factors can be multiplied together. Note that the combinatorics of factors ${{\gamma_i + J_\text{P} - 1}\choose{J_\text{P} - 1}}$ and $\frac{
	{\gamma_i}!}{{n^{(\text{P})}_{i,1}}! \cdots \; {n^{(\text{P})}_{i,J_\text{P}}}!}$ are explained in MODL \citep{Boulle_2006}.

@@

Finding optimal discretization policies according to equation~\ref{eq:opt_prob} via dynamic programming requires long computation times when the dataset has more than \num{100} variables.
The runtime for the MDL approach is even more severe.
Approximation approaches are reasonable alternatives for datasets with more variables, including a greedy heuristic~\citep{Friedman_1996}.
Approximations can also be applied during dynamic programming when solving equation~\ref{eq:opt_prob} \citep{Boulle_2006}.

>>>>

The two factors on the right hand side come from the second principle: all distributions of values of the parents of $\cX$ in a given interval are equiprobable.
The fourth principle is that the distributions for each interval are independent, so the factors can be multiplied together. Note that the combinatorics of factors ${{\gamma_i + J_\text{P} - 1}\choose{J_\text{P} - 1}}$ and ${
	{\gamma_i}!}/{{n^{(\text{P})}_{i,1}}! \cdots \; {n^{(\text{P})}_{i,J_\text{P}}}!}$ are explained in MODL \citep{Boulle_2006}.

@@

Finding optimal discretization policies according to equation~\ref{eq:opt_prob} via dynamic programming requires long computation times when the dataset has more than \num{100} variables.
The runtime for the MDL approach is even more severe.
Approximation approaches are reasonable alternatives for datasets with more variables, including a greedy heuristic~\citep{Friedman_1996}.
Approximations can also be applied during dynamic programming when solving Equation~\ref{eq:opt_prob} \citep{Boulle_2006}.
